\begin{thebibliography}{20}

\item[\textbullet] 书籍：

\bibitem{manual} Leslie Lamport. 
  \newblock \emph{\LaTeX: A Document Preparation System}.  
  \newblock Addison-Wesley, Reading, Massachusetts, second edition, 1994, ISBN~0-201-52983-1.
  
\bibitem{texbook} Donald~E. Knuth. 
  \newblock \textit{The \TeX book}, Volume~A of \textit{Computers and Typesetting}, 
  \newblock Addison-Wesley, Reading, Massachusetts, second edition, 1984, ISBN~0-201-13448-9.

\bibitem{companion} Frank Mittelbach, Michel Goossens, Johannes Braams, David Carlisle, Chris Rowley. 
  \newblock \emph{The \LaTeX\ Companion}.  
  \newblock Addison-Wesley, Reading, Massachusetts, second edition, 2004, ISBN~0-201-36299-6.

\bibitem{graphicscompanion} Michel Goossens, Sebastian Rahtz and Frank Mittelbach. 
  \newblock \emph{The \LaTeX\ Graphics Companion}. 
  \newblock Addison-Wesley, Reading, Massachusetts, 1997, ISBN~0-201-85469-4.

\bibitem{leoliu} 刘海洋.
  \newblock \emph{\LaTeX\ 入门}. 
  \newblock 电子工业出版社, 北京, 2013, ISBN~978-7-121-20208-7 

\item[\textbullet] \TeX\ 发行版内置的资源（除宏包帮助手册之外的一些文档），
  可以在本地使用 \texttt{texdoc} 命令查找，也可以在 CTAN 上找到：

\bibitem{usrguide} \LaTeX3 Project Team.
  \newblock \emph{\LaTeXe\ for authors}.\\
  \newblock \CTAN|macros/latex/doc/usrguide.pdf| (\texttt{texdoc usrguide})

\bibitem{clsguide} \LaTeX3 Project Team.
  \newblock \emph{\LaTeXe\ for Class and Package writers}. \\
  \newblock \CTAN|macros/latex/doc/clsguide.pdf| (\texttt{texdoc clsguide})

\bibitem{fntguide} \LaTeX3 Project Team.
  \newblock \emph{\LaTeXe\ Font Selection}. \\
  \newblock \CTAN|macros/latex/doc/fntguide.pdf| (\texttt{texdoc fntguide})

\bibitem{latex2e} Karl Berry, Jim Hefferon, Vincent Bela\"{\i}che.
  \newblock \emph{\LaTeXe: An unofficial reference manual}. \\
  \newblock \CTAN|info/latex2e-help-texinfo/latex2e.pdf| (\texttt{texdoc latex2e})

\bibitem{l2tabu} J\"{u}rgen Fenn.
  \newblock \emph{An essential guide to \LaTeXe\ usage: Obsolete commands and packages} (English translation). \\
  \newblock \CTAN|info/l2tabu/english/l2tabuen.pdf| (\texttt{texdoc l2tabuen})

\bibitem{symbols} Scott Pakin.
  \newblock \emph{The Comprehensive \LaTeX\ Symbol List}. \\
  \newblock \CTAN|info/symbols/comprehensive/symbols-a4.pdf| (\texttt{texdoc symbols-a4})

\item[\textbullet] CTAN 上的其它网络资源：

\bibitem{catalogue} Graham Williams.
  \newblock \emph{The \TeX\ Catalogue (Preface CTAN Edition)}.\\
  \newblock \CTAN|help/Catalogue/catalogue.html|

\bibitem{survey} Stephen~G. Hartke.
  \newblock \emph{A Survey of Free Math Fonts for \TeX\ and \LaTeX}.\\
  \newblock \CTAN|info/Free_Math_Font_Survey/survey.pdf|

\item[\textbullet] 其它网络渠道可获得的资源：

\bibitem{fontcatalogue} Palle J{\o}rgensen.
  \newblock \emph{The \LaTeX\ font catalogue}, a font catalogue of \LaTeX\ font packages.\\
  \newblock \url{http://www.tug.dk/FontCatalogue/}

\bibitem{ltxprimer} Indian \TeX\ user group. 
  \newblock \emph{\LaTeX\ Tutorials: A primer}. \\
  \newblock \url{http://www.tug.org/twg/mactex/tutorials/ltxprimer-1.0.pdf}

\bibitem{lnotes} 黄新刚. 
  \newblock \emph{雷太赫排版系统简介 (\LaTeX\ Notes) 第二版}. \\
  \newblock \url{http://dralpha.altervista.org/zh/tech/lnotes2.pdf} \\
  （旧版可用 \texttt{texdoc latex-notes-zh-cn}）

\end{thebibliography}

\endinput